Kyoto VR MQP Paper First Draft

### 2019-09-23 paper.tex
working on editour section

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone harware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a webcam and laptop.

ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
app on native hardware without the need for an emulator. In the root directory
of your project, you can launch a Node server with the command \texttt{npm
start}. From here, you can input the provided URL into the Viro Media app. This
will quickly download the code, graphics, and 3D object files from the server
and launch a functional version of the app \autocite{viro-testbed2019}. This
allowed us to get a real AR app up and running on our devices much more easily
than any of the other frameworks/engines we explored. Unfortunately, the test
bed app was somewhat unreliable based on our experience; the test bed would
frequently crash or would not be able to download the files from the Node
server. The most reliable way to test our app was to compile a binary and
manually install it onto our devices, which completely defeats the purpose of
the test bed app.

@@

We were tasked with building an AR mobile app that enhances the experience of
visiting Kinkaku-ji, or the Golden Pavilion. As of September 2019, Kinkaku-ji
is the second-most visited site in Kyoto---second only to Kyoto Station
\autocite{japanguide2019}.

@@

@@

In Editour, the frontend alone was already around three thousand lines of
vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
the growing code complexity more manageable. Excluding Node.js modules, the only
external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps \autocite{leafletjs}. We did not use any libraries
for developing frontends like Facebook's React or Google's Angular. Instead,
all of the complex UI interactions were handled by modifying the DOM directly
with JavaScript's built-in functionality. Furthermore, we did not use any
advanced frontend build tools such as Rollup, webpack or Parcel. This was
likely an appropriate decision for a JavaScript project of this scope, but if
we were to continue to develop Editour, UI libraries and frontend build tools
would be something to consider. With these changing requirements, the Editour
was becoming onerous to maintain at this stage of the project.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This unique region also prompted us to think about what UI
behavior made the most sense if a user were to walk into a region, walk out and
then in again. We decided that it was awkward if the audio restarted upon
re-entering a region, since the audio would still be playing once a user left
the region. The region at the bottom surrounding our domitories was added for
our convenience, allowing us to test the app while we were away from the lab.
As we began to implement more complex UI that changed based on GPS position in
various ways, directly taking the tour by walking around was an invaluable way
to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
in the late stages of the project. Having a way to regularly run field tests
was integral to polishing the app in time before we revisited Kinkaku-ji.
Because the Editour was flexible enough to easily swap out media and add
regions to the tour, the Editour proved itself to be as helpful for testing as
it was for crafting the final tour that could be taken at Kinkaku-ji.

>>>>

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone harware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a laptop webcam.

As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
rapidly testing your ViroReact app on native hardware without the need for an
emulator. In the root directory of your project, you can launch a Node server
with the command \texttt{npm start}. From here, you can input the provided URL
into the Viro Media app. This will quickly download the code, graphics, and 3D
object files from the server and launch a functional version of the app
\autocite{viro-testbed2019}. This allowed us to get a real AR app up and
running on our devices much more easily than any of the other
frameworks/engines we explored. Unfortunately, the test bed app was somewhat
unreliable based on our experience; the test bed would frequently crash or
would not be able to download the files from the Node server. The most reliable
way to test our app was to compile a binary and manually install it onto our
devices, which completely defeats the purpose of the test bed app.

@@

We were tasked with building an AR mobile app that enhances the experience of
visiting Kinkaku-ji, also known as the Golden Pavilion. As of September 2019,
Kinkaku-ji is the second-most visited site in Kyoto---second only to Kyoto
Station \autocite{japanguide2019}.

@@

\subsubsection{Editing a Tour}
\label{sec:editingATour}

The user can easily create a new region by shift-clicking, and then clicking
points on the map. To terminate the polygon, the user must shift-click again.
A user can only terminate the polygon after two points have been placed to
prevent the user from drawing a region with an area of zero. Once a region is
created, a region card appears in the side bar. From here, the user can edit
anything about the region. From here, the user can edit anything about the
region.

The top of the region card displays the region name in bold text. By clicking
on the region name, the map will pan and zoom to frame the region in the center
of the screen. This is useful if there are many regions. To the right of the
region name, there are two arrow buttons, one pointed up and another pointed
down. This allows the user to reorder the regions in the column. This was one
of the features that was added late into development in order to adapt to an
important change in the tour app, ARuko. This is discussed in
Section~\ref{sec:adobeXdDesign}.

In the region card, there are four multicolored expandable ``subcards'' that
allow the user to edit different information about each region. Since there can
be many region cards in the column, it was important to be able to collapse
each section. Collapsing the subcards gives the user enough room to see
multiple region cards at a time.

The first subcard is the ``Rename'' subcard, which is fairly self-explanatory.
This section expands to reveal a textbox, allowing the user to rename the
region after clicking ``Okay'' or hitting the enter key. (There are multiple
places in the UI where a textbox is immediately adjacent to a ``Confirm''
button.  We made sure all of these can be triggered by simply hitting enter,
since this is common when filling out forms.)

The second subcard is slightly involved. Expanding the ``Media'' subcard by
clicking on the green bar will reveal a bevy of options for augmenting the
audio, images and text to be associated with that region of the tour. From
here, the user can upload an audio file and multiple image files from his or
her hard drive with the two file-select fields. If the tour has been downloaded
as a server, the names of the files already present on the server will appear
as cards with `X' buttons. This allows the user to remove images or audio from
that region even after the tour has been uploaded.

The third subcard is the ``Edit'' subcard. This subcard can be revealed in one
of two ways. The first way is by clicking on the yellow bar labeled ``Edit'',
which is the same for all subcards. Alternatively, the user can also click
directly on the region on the map. The region will flash yellow and be scrolled
into view to let the user know which region was clicked on. Both of these
methods will enable editing mode, whereby the user can directly manipulate the
vertices that make up the region. Blue circles appear on top of each vertex,
and red circles appear at the midpoint of each edge. Clicking on a red midpoint
will add an additional vertex at that midpoint. Dragging one of the blue
vertices will do as you might expect---move the vertex around. The latitude and
longitude are updated in the ``Edit'' subcard as the user drags the vertex
around. Clicking on the vertex directly will create a blue pin-shaped marker
that the user can also drag around. Clicking on the coordinate box in the
subcard will also create this blue pin-shaped marker; the map will also pan to
this coordinate. The user can also delete vertices in the same way that files
can be deleted from the ``Media'' subcard by clicking on the `X' button. If there
are exactly three points in a region, the `X' buttons will be ``grayed-out'',
preventing the user from deleting any more points (since a polygon must consist
of at least three points.)

The third subcard is the ``Delete'' subcard. When revelead, another button will
appear labeled ``Really Delete''. The action can be canceled by collapsing the
subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
from accidentally deleting a region he or she did not mean to.

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process. If a 200 or 201 is returned from the
server, a ``Success'' message will appear. If there was some problem, the error
message returned by the server is displayed in this box instead. Since
uploading, downloading and deleting are all network-related operations, it
makes sense to include this message box for each card.

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking on
one of these blue buttons will fill the textbox in with the correct name. Before
this feature was implemented, the user had to correctly type the name of the
saved tour into the textbox in order to retrieve it. The user is still free to
do this, but the buttons make this easier and less error-prone.

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla Javascript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience..
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. The region at the bottom surrounding our domitories was added
for our convenience, allowing us to test the app while we were away from the
lab.  As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.
